Understanding domestic abuse - Pathways to Impact

### 2019-07-23 pathways_to_impact.tex
Anna update

In the second year of the proposal we will hold a 1-day impact summit at Warwick Business School's London Shard venue. This will be funded by the Warwick Business School Impact Fund, and potentially the ESRC Impact Acceleration Account. We will host the National Police Chiefs' Council lead for Domestic Abuse, Deputy Chief Constable Louisa Rolfe (who is also at West Midlands Police), and Members of Parliament from the Home Affairs Committee domestic abuse inquiry. The summit will be a 50/50 academic / practitioner mix. We will contact, early in the project, [Insert list of charities in this sector, Women's Aid, Refuge, Safe Lives, National Centre for Domestic Abuse] and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.

@@

Although a high-profile ``launch'' event at the Shard will attract attention, it is the continuous week-on-week contact with our impact partners that we think will deliver the legacy impact for this project.

Within Lloyds Bank, we will work with Martin King, Head of Customer Vulnerability. Warwick already has a relationship with King's team in CI Stewart's work on the effects of gambling, which was completed using micro-level transaction data from millions of account holders. Key issues here are work on coercion and control, and having sufficient financial resilience to escape an abusive relationship and being able to make the decision to report an abuser. Our day-to-day contact at Lloyds is Dr David Leake, Head of the Behavioural Insights Team. We will present the findings from all four programmes to the Lloyds Vulnerability Team in six-monthly briefings, and work to integrate insight from the research into the Lloyds environment.

@@

PI Mullett will spend half of his time of the project leading the impact activity and takes overall responsibility of delivering the impact programme. Mullett has worked extensively on the impact programme from the ESRC funded ``Accumulating to Choose'' programme, with the Financial Conduct Authority. CI Stewart will also spend half of his time of the project on the impact activity. Stewart has significant experience of impact acitivites in the domain of financial decision making with Lloyds Banking Group, Barclays Bank, and the UK Finance Association. Postdoc Trendl will be fully involved in the impact programme. This is an important part of the professional development for an early career researcher, and will allow her to establish a network of independent contacts.

>>>>

In the second year of the proposal we will hold a 1-day impact summit at Warwick Business School's London Shard venue. This will be funded by the Warwick Business School Impact Fund, and potentially the ESRC Impact Acceleration Account. We will host the National Police Chiefs' Council lead for Domestic Abuse, Deputy Chief Constable Louisa Rolfe (who is also at WMP), and Members of Parliament from the Home Affairs Committee domestic abuse inquiry. The summit will be a 50/50 academic / practitioner mix. We will contact, early in the project, domestic abuse charities Women's Aid, Refuge, Safe Lives, and National Centre for Domestic Abuse, and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.

@@

Although a high-profile dissemination event at the Shard will attract attention, it is the continuous week-on-week contact with our impact partners that we think will deliver the legacy impact for this project.

Within Lloyds Bank, we will work with Martin King, Head of Customer Vulnerability. Warwick already has a relationship with King's team in CI Stewart's work on the effects of gambling, which was completed using micro-level transaction data from millions of account holders. Key issues here are work on coercion and control, and how financial resilience affects the decision to contact the police and escape the cycle of abuse. Our day-to-day contact at Lloyds is Dr David Leake, Head of the Behavioural Insights Team. We will present the findings from all four programmes to the Lloyds Vulnerability Team in six-monthly briefings, and work to integrate insight from the research into the Lloyds environment.

@@

PI Mullett will spend half of his time of the project leading the impact activity and takes overall responsibility of delivering the impact programme. Mullett has worked extensively on the impact programme from the ESRC funded ``Accumulating to Choose'' programme, with the Financial Conduct Authority. CI Stewart will also spend half of his time of the project on the impact activity. Stewart has significant experience of impact activities in the domain of financial decision making with Lloyds Banking Group, Barclays Bank, and the UK Finance Association. Postdoc Trendl will be fully involved in the impact programme. This is an important part of the professional development for an early career researcher, and will allow her to establish a network of independent contacts.
